Weakly Nonlinear MRI: Notes

### 2014-03-14 notes/mri_notes.tex
more expansion
a little more
a lot more
final equation

Note that this differs from what Umurhan+ find, although it shouldn't. The sign of the $\chi$ term, the $\partial_z$ in front of it, and the inclusion of the last term are all different. \\

@@

>>>>

Note that this differs from what Umurhan+ find, although it shouldn't. The sign of the $\mathcal{X}$ term, the $\partial_z$ in front of it, and the inclusion of the last term are all different. \\

@@

$\partial_z^4 = \partial_z^4 + 4\epsilon \partial_z^3 \partial_Z + 6 \epsilon^2 \partial_z^2 \partial_Z^2 + 4 \epsilon^3 \partial_z \partial_Z^3 + \epsilon^4\partial_Z^4$ \\

Thus $\mathcal{L}$ becomes $\mathcal{L^*}$, defined as: \\

$\mathcal{L^*} = \mathcal{L}_0 \, + \, \mathcal{L}_1\partial_z \,+ \, \epsilon\mathcal{L}_1 \partial_Z \, + \, \mathcal{L}_2\partial_z^2 \, + \, \epsilon^2\mathcal{L}_2\partial_Z^2 \, + \, 2\epsilon\mathcal{L}_2\partial_z\partial_Z \, + \, \mathcal{L}_3\partial_z^3 \, +\, 3\epsilon \mathcal{L}_3 \partial_z^2 \partial_Z \,+\, 3 \epsilon^3\mathcal{L}_3\partial_Z^2\partial_z \,+\, \epsilon^3\mathcal{L}_3\partial_Z^3 \, + \, \mathcal{L}_4\partial_z^4 \, + \, 4 \epsilon \mathcal{L}_4 \partial_z^3 \partial_Z \, + \, 6 \epsilon^2\mathcal{L}_4 \partial_z^2 \partial_Z^2 \, + \, 4 \epsilon^3 \mathcal{L}_4 \partial_Z^3\partial_z \, + \, \epsilon^4\mathcal{L}_4\partial_Z^4$ \\

This is just $\mathcal{L}$ plus 10 terms. Grouping those terms by $\mathcal{O}(\epsilon)$: \\

$\mathcal{L^*} = \mathcal{L} + \epsilon\mathcal{L}_1\partial_Z \, + \, 2\epsilon\mathcal{L}_2\partial_z\partial_Z \, + \, 4 \epsilon\mathcal{L}_4\partial_z^3 \partial_Z \, + \, 3\epsilon\mathcal{L}_3\partial_z^2\partial_Z \, + \, \epsilon^2\mathcal{L}_2\partial_z^2 \, + \, 3\epsilon^2\mathcal{L}_3\partial_Z^2\partial_z \, + \, 6\epsilon^2\mathcal{L}_4 \partial_z^2 \partial_Z^2 \, + \, \epsilon^3\mathcal{L}_3\partial_Z^3 \, + \, 4 \epsilon^3\mathcal{L}_4\partial_z^3 \partial_z \, + \, \epsilon^4\mathcal{L}_4\partial_Z^4 $ \\

Note that we have the same terms as the $\widetilde{\mathcal{L}}_1$ operator in Umurhan+, but we do not have the same terms as their $\widetilde{\mathcal{L}}_2$. \\

The $\partial_z\mathcal{X}$ and $\partial_z^3\mathcal{L}_3$ terms become: \\

$-\epsilon^2\partial_z\mathcal{X} \to \left(-\epsilon^2 - \epsilon^3\partial_Z\right)\mathcal{X}$ \\

$-\epsilon^2\partial_z^3\mathcal{L}_3 \to \left(-\epsilon^2\partial_z^3 - 3\epsilon^3\partial_z^2\partial_Z - 3\epsilon^4\partial_z\partial_Z^2 - \epsilon^5\partial_Z^3\right)\mathcal{L}_3$ \\

And $\mathcal{D}$ becomes: \\

$\mathcal{D} \to \left[\begin{matrix}
\nabla^2 & 0 & 0 & 0 \\
0 & 1& 0 & 0 \\
0 & 0 & 1 & 0\\
0 & 0 & 0 & 1 \\
\end{matrix}\right] + \left(\epsilon^2\partial_Z^2 + 2\epsilon\partial_z\partial_Z\right)\left[\begin{matrix}
1 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\ \end{matrix}\right]$ \\

We will call this $\mathcal{D} + \left(\epsilon^2\partial_Z^2 + 2\epsilon\partial_z\partial_Z\right)\mathcal{D^*}$. \\

Our final equation is: \\

$\left(\partial_t + \epsilon^2 \partial_T \right)\mathcal{D}\mathbf{V} \, + \, \left(\partial_t + \epsilon^2\partial_T\right)\left(\epsilon^2\partial_Z^2 + 2\epsilon\partial_z\partial_Z\right)\mathcal{D^*}\mathbf{V} \, + \, \mathbf{N} \, = \, \mathcal{L}\mathbf{V} \, + \, \epsilon\widetilde{\mathcal{L}}_1\partial_Z\mathbf{V} \, + \, \epsilon^2\widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V} \, + \, \epsilon^3\widetilde{\mathcal{L}}_3\partial_Z^3\mathbf{V} \, + \, \epsilon^4\widetilde{\mathcal{L}}_4\partial_Z^4\mathbf{V} \, - \, \epsilon^2\partial_z\mathcal{X}\mathbf{V} \, - \epsilon^3\partial_Z\mathcal{X}\mathbf{V} \, - \, \epsilon^2\partial_z^3\mathcal{L}_3\mathbf{V} \, - \, 3\epsilon^3\partial_z^2\partial_Z\mathcal{L}_3\mathbf{V} \, - \, 3\epsilon^4\partial_z\partial_Z^2\mathcal{L}_3\mathbf{V} \, - \, \epsilon^5\partial_Z^3\mathcal{L}_3\mathbf{V}$ \\

$\widetilde{\mathcal{L}}_1 = \mathcal{L}_1 + 2\mathcal{L}_2\partial_z + 3\mathcal{L}_3\partial_z^2 + 4\mathcal{L}_4\partial_z^3$ \\

$\widetilde{\mathcal{L}}_2 = \mathcal{L}_2 + 3\mathcal{L}_3\partial_z + 6\mathcal{L}_4\partial_z^2$ \\

$\widetilde{\mathcal{L}}_3 = \mathcal{L}_3 + 4\mathcal{L}_4\partial_z$ \\

$\widetilde{\mathcal{L}}_4 = \mathcal{L}_4$ \\

To $\mathcal{O}(\epsilon^2)$ this becomes: \\

$\partial_t\mathcal{D}\mathbf{V} \, + \, \epsilon^2 \partial_T \mathcal{D}\mathbf{V} \, + \, \epsilon^2\partial_Z^2\partial_t\mathcal{D^*}\mathbf{V} \, + \, 2\epsilon\partial_z\partial_Z\partial_t\mathcal{D^*}\mathbf{V} \, + \, \mathbf{N} \, = \, \mathcal{L}\mathbf{V} \, + \, \epsilon\widetilde{\mathcal{L}}_1\partial_Z\mathbf{V} \, + \, \epsilon^2\widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V} \, - \, \epsilon^2\partial_z\mathcal{X}\mathbf{V} \, - \, \epsilon^2\partial_z^3\mathcal{L}_3\mathbf{V} \, + \, \mathcal{O}(\epsilon^3)$
